|

### 2021-12-14 01-Chp-Background.Rmd
Update table captions to new style

<!----------------------------------------------------------------------------->
(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013]

@@

(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]

@@

(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.

@@

<!----------------------------------------------------------------------------->
(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.

>>>>

<!----------------------------------------------------------------------------->
(ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia and vascular dementia.__ - These published criteria[@edition2013] are commonly used to defined dementia outcomes. <!-- TODO Need to finish this sentence and explan criteria better -->

@@

(ref:lipidLevels-caption) __Classification of blood lipid levels__ - Category cut-offs for different lipid fractions according to the National Cholesterol Education Program guidelines.[@national2002third]

@@

(ref:statinOverview-caption) __Overview of common statins__ -  There are several commonly-prescribed statins used to treat hypercholesterolemia. Their approval date (US), properties and lipid-lowering effect are described here.

@@

<!----------------------------------------------------------------------------->
(ref:lipidTreatments-caption) __Summary of available treatments for hyperlipidaemia.__

### 2021-12-14 03-Chp-Systematic-Review-Methods.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion
Update table captions to new style

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results. 
&nbsp;

@@

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) Summary of systematic search by topic. The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).

(ref:searchOverview-scaption) searchOverview

@@

<!----------------------------------------------------------------------------->
(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric[@mchugh2012]

>>>>

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.

@@

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) __Summary of systematic search by topic__ - The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).

(ref:searchOverview-scaption) Summary of systematic search by topic

@@

<!----------------------------------------------------------------------------->
(ref:gwet-caption) __Ranges for Gwet's AC1__ - To aid the interpretation of inter-/intra-rater reliability, I used a published set of suggested categories for Gwet's AC1.[@mchugh2012]

### 2021-12-14 05-Chp-CPRD-Analysis.Rmd
Update table captions to new style

# Primary analysis of lipid-regulating agents and dementia outcomes {#cprd-analysis-heading}

@@

<!--------------------------------------------------------------------------->
(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._). Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.

@@

<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model. The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].

(ref:covariateDef-scaption) Covariates adjusted for.

@@

<!----------------------------------------------------------------------------->
(ref:followUp-caption) Summary of number of events, years at risk and crude rates per 100,000 participant-years-at-risk stratified by dementia outcome and drug class of interest.

(ref:followUp-scaption) Crude rates, stratified by outcome and drug class of interest.

```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
```
(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.

(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type

@@

<!----------------------------------------------------------------------------->
(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry

@@

(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.

>>>>

# Primary analysis of lipid-regulating agents and dementia outcomes in the CPRD {#cprd-analysis-heading}

@@

<!--------------------------------------------------------------------------->
(ref:readExample-caption) __Example of CPRD Read code hierarchy__ - Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context. The example shown illustrates how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).

@@

<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) __Definitions of covariates adjusted for in the analysis__ - The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].

(ref:covariateDef-scaption) Definitions of covariates adjusted for in the analysis

@@

<!----------------------------------------------------------------------------->
(ref:followUp-caption) __Crude rates, stratified by outcome and drug class of interest__ - The number of events, years at risk and crude rates per 100,000 participant-years-at-risk stratified by dementia outcome and drug class of interest are presented below.

(ref:followUp-scaption) Crude rates, stratified by outcome and drug class of interest

```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
```

(ref:cprdCharacteristics-caption) __Patient characteristics by drug class__ - Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:cprdSSA-caption) __Summary of treatment change__ - The number of participants who stopped, switched or added treatments was calculated, stratified by initial LRA type.

(ref:cprdSSA-scaption) Summary of treatment change

@@

<!----------------------------------------------------------------------------->
<!-- TODO Check table caption -->

(ref:diagnosisType-caption) __Frequency of diagnoses by grouped year of cohort entry__

@@

<!-- TODO Check this table title -->

(ref:statinTypeTable-caption) __Summary of statin properties (lipophilicity vs hydrophilicity)__, by grouped year of prescription.

### 2021-12-14 06-Chp-IPD-Analysis.Rmd
Update table captions to new style

<!----------------------------------------------------------------------------->
(ref:mainEffectDem-cap) IPD meta-analysis (Model 1) of all-cause dementia outcomes, stratified by lipid fraction

(ref:mainEffectDem-scap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction

@@

<!----------------------------------------------------------------------------->
(ref:mainEffectVad-cap) IPD meta-analysis (Model 1) of vascular dementia outcomes, stratified by lipid fraction. Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts.

(ref:mainEffectVad-scap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction

@@

<!----------------------------------------------------------------------------->
(ref:whitehallComparisonDementia-cap) Comparison of results across the two analyses of the Whitehall II cohort for the all-cause dementia outcome.

(ref:whitehallComparisonDementia-scap) Comparison of results across the two analyses of the Whitehall II cohort

@@

<!----------------------------------------------------------------------------->
(ref:whitehallComparisonAd-cap) Comparison of results across the two analyses of the Whitehall II cohort for the Alzheimer's disease outcome.

(ref:whitehallComparisonAd-scap) Comparison of results across the two analyses of the Whitehall II cohort

>>>>

<!----------------------------------------------------------------------------->
(ref:mainEffectDem-cap) __IPD meta-analysis of all-cause dementia__ - Using Model 1 (adjusted for age, sex, smoking, alcohol, education and diabetes), an IPD random-effects meta-analysis was applied to investigate the association of a 1-SD increase in each lipid fraction with all-cause dementia outcomes.

(ref:mainEffectDem-scap) IPD meta-analysis of all-cause dementia

@@

<!----------------------------------------------------------------------------->
(ref:mainEffectVad-cap) __IPD meta-analysis of vascular dementia__ - Using Model 1 (adjusted for age, sex, smoking, alcohol, education and diabetes), an IPD random-effects meta-analysis was applied to investigate the association of a 1-SD increase in each lipid fraction with vascular dementia outcomes. Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts (see Table \@ref(tab:covariateSummary-table)).

(ref:mainEffectVad-scap) IPD meta-analysis of vascular dementia

@@

<!----------------------------------------------------------------------------->
(ref:whitehallComparisonDementia-cap) __Comparison of two analyses of the Whitehall II cohort (all-cause dementia)__ - A published analysis by Tynkkynen _et al._[@tynkkynen2018] had previously examined the association of lipid fractions and all-cause dementia in the Whitehall II cohort. The results of the two analyses are shown above and were broadly comparable, except for the triglyceride fraction. Potential reasons for this discrepancy are discussed in the main text.

(ref:whitehallComparisonDementia-scap) Comparison of two analyses of the Whitehall II cohort (all-cause dementia)

@@

<!----------------------------------------------------------------------------->
(ref:whitehallComparisonAd-cap) __Comparison of two analyses of the Whitehall II cohort (Alzheimer's disease)__ - A published analysis by Tynkkynen _et al._[@tynkkynen2018] had previously examined the association of lipid fractions and Alzheimer's disease in the Whitehall II cohort. The results of the two analyses are shown above and were broadly comparable.

(ref:whitehallComparisonAd-scap) Comparison of two analyses of the Whitehall II cohort (Alzheimer's disease)

### 2021-12-14 07-Chp-Triangulation.Rmd
Update table captions to new style

# Aetiological triangulation across new and existing evidence sources {#tri-heading}

@@

(ref:exampleDirection-scap) Illustration of calculating the absolute direction of biases, based on bias type

@@

####	Assign modifying values to risk/direction of bias
<!-- TODO Note that they are on the log scale, and that this requires the results to be on the log scale too! - Lines 45-50 of addbias -->

>>>>

# Aetiological triangulation across new and existing evidence sources: a qualitative and quantitative approach {#tri-heading}

@@

(ref:exampleDirection-scap) Calculating the absolute direction of biases, based on bias type

@@

####	Assign modifying values to risk/direction of bias {#tri-bias-assign}
<!-- TODO Note that they are on the log scale, and that this requires the results to be on the log scale too! - Lines 45-50 of addbias -->

### 2021-12-14 front-and-back-matter/99-appendices.Rmd
Update table captions to new style

<!----------------------------------------------------------------------------->
(ref:medRes-caption) Publication status of medRxiv preprints deposited in July 2019, allowing for a two-year lag

@@

(ref:wosDatabases-caption) Summary of Web of Science databases searched. The contents of the Web of Science core collection can vary depending on an institution's subscription, and so detailing the exact databases and ranges searched is important.

(ref:wosDatabases-scaption) Summary of Web of Science databases searched.

@@

(ref:searchOverviewAppendix-caption) Summary of number of records identified in each database searched

(ref:searchOverviewAppendix-scaption) searchOverviewAppendix

@@

(ref:searchHitsMedline-caption) Overview of the full Medline search strategy.

@@

(ref:searchHitsEmbase-caption) Overview of the full Embase search strategy.

@@

(ref:searchHitsPI-caption) Overview of the full PyscINFO search strategy.

@@

(ref:searchHitsCentral-caption) Overview of the full CENTRAL search strategy.

@@

(ref:searchHitsWos-caption) Overview of the full Web of Science search strategy.

@@

(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]

@@

<!----------------------------------------------------------------------------->
(ref:prismaTab-caption) __PRISMA Checklist__

@@

(ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia

@@

(ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease

@@

(ref:minFU-cap) Diagram illustrating the design of two studies. Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up. In contrast, Panel B illustrates the time- varying analysis used in Chapter \@ref(cprd-analysis-heading), which makes it challenging to define an unbiased minimum period of follow-up.

@@

With these caveats in mind, below I present a sensitivity analysis of the association of statins with dementia outcomes, enforcing a minimum 10-year period of follow-up from statin initiation in those prescribed a statin.

<!----------------------------------------------------------------------------->
(ref:cprdMinFu-cap) Sensitivity analysis showing the results of a re-analysis of the CPRD data enforcing a minimum follow-up period of 10 years in the statin group. Events occurring within 10 years of inititating statins were discarded, but the participant-time-at-risk was maintained. No minimum follow-up period was applied in those never taking a statin, due to the difficulties in defining the start date for the follow-up period, as discussed in the text above.

(ref:cprdMinFu-scap) Sensitivity analysis of the CPRD data with a 10 year minimum period of follow-up.

```{r cprdMinFu, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdMinFu-cap)', out.width='100%', fig.scap='(ref:cprdMinFu-scap)'}
knitr::include_graphics(file.path("figures/hold.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:missingMatrix-caption) Overview of missing data across covariates (described as N (%)) included in IPD analysis. Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.

(ref:missingMatrix-scaption) missingMatrix

@@

<!----------------------------------------------------------------------------->
(ref:ipdDementiaDef-caption) Definition of dementia outcomes across cohorts included in the individual participant data meta-analysis. Note the codes used to define dementia and related outcomes in the HES data as part of the Whitehall II cohort were taken from a previously published analysis.[@russ2014]

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:addTable1-caption) Distributions of bias, defined by position and variance terms, assigned by four independent experts to attrition and detection bias in a single study. This data was obtained from a previous publication,[@turner2009] and represents an illustrative subset of the larger dataset.

(ref:addTable1-scaption) addTable1

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:addTable2-caption) Position and variance values for two example bias domains (attritiona and detection), obtained by averaging the absolute of the values contained in \@ref(tab:addTable3-table) across the four reviewers.

(ref:addTable2-scaption) addTable1

@@

I then took the average and maximum of the expert-averaged position and variance values. The results of this for the example data are presented in Table \@ref(tab:addTable3-table).

&nbsp;<!----------------------------------------------------------------------->  
(ref:addTable3-caption) Mean and maximum of position and variance values desribed in Table \@ref(tab:addTable3-table)

(ref:addTable3-scaption) addTable1

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:turnerEstimates-caption) Mean and maximum distributions for bias and indirectness obtained from data resulting from the elicitation exercise reported in _Turner et al_[@turner2009]. Note I did not calculate values for additive indirectness, as in my analysis, all indirectness was assumed to be proportional.

(ref:turnerEstimates-scaption) turnerEstimates

@@

(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias. Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels

(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
```

(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias. Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels

(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.

@@

<!-- TODO Need to complete this sections -->
The robvis package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.

@@

\blandscape
<!----------------------------------------------------------------------------->
(ref:biasData-caption) First five assessments contained in `data_rob2`, an example dataset for the Risk of Bias 2 tool for randomised controlled trials available via the `robvis` package.

(ref:biasData-scaption) biasData

@@

<!----------------------------------------------------------------------------->
(ref:biasDirectionData-caption) Example data illustrating the structure required for bias direction plots. $d_ij$, $d_id$, and $d_it$ define the extent (Serious, Moderate, Low), direction (right or left), and type (additive or proportional) of bias in the $i$th domain. Note that, because of the wide nature of the data, I have abbreviated the data in order to display it. A key for interpreting the data can be found below the table.

(ref:biasDirectionData-scaption) biasDirectionData

@@

<!----------------------------------------------------------------------------->
(ref:robSummary-cap) Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above. Note that this plot is unweighted and shows the _proportion of studies_ at each level of bias, but an option exists with `robvis` to create a barplot weighted by the _proportion of evidence_ at each level of bias.

@@

<!----------------------------------------------------------------------------->
(ref:robTraffic-cap) Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.

>>>>

<!----------------------------------------------------------------------------->
(ref:medRes-caption) __Publication status of medRxiv preprints__ - The publication status of medRxiv preprints deposited in July 2019 was assessed in July 2021 (allowing for a two-year lag) and found that a substantial proportion remained unpublished.

@@

(ref:wosDatabases-caption) __Summary of Web of Science databases searched__ - The contents of the Web of Science core collection can vary depending on an institution's subscription, and so detailing the exact databases and ranges searched is important.

(ref:wosDatabases-scaption) Summary of Web of Science databases searched

@@

(ref:searchOverviewAppendix-caption) __Summary of number of records identified in each database searched__ - The full line-by-line search results for the each database, are presented in subsequent tables. Note there was substantial duplication across databases, resulting in several thousand duplicates being removed prior to title and abstract screening.

(ref:searchOverviewAppendix-scaption) Summary of number of records identified in each database searched

@@

(ref:searchHitsMedline-caption) __Medline search strategy__ - Full list of search terms used to identify relevant records in the Medline bibliographic database. The number of records returned per search term is also displayed.

@@

(ref:searchHitsEmbase-caption) __Embase search strategy__ - Full list of search terms used to identify relevant records in the Embase bibliographic database. The number of records returned per search term is also displayed.

@@

(ref:searchHitsPI-caption) __PyscINFO search strategy__ - Full list of search terms used to identify relevant records in the PyscINFO bibliographic database. The number of records returned per search term is also displayed.

@@

(ref:searchHitsCentral-caption) __CENTRAL search strategy__ - Full list of search terms used to identify relevant records in the CENTRAL bibliographic database. The number of records returned per search term is also displayed. Note that at the last step, I applied a manual filter via the CENTRAL web interface to limit the search to primary studies.

@@

(ref:searchHitsWos-caption)  __Web of Science search strategy__ - Full list of search terms used to identify relevant records in the Web of Science bibliographic database. The number of records returned per search term is also displayed.

@@

(ref:mrTool-caption) __Mendelian randomisation risk-of-bias assessment tool__ - A copy of the tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]

@@

<!----------------------------------------------------------------------------->
(ref:prismaTab-caption) __PRISMA Checklist__ - Following best practice guidelines, the Section/Table/Figure number were important details on the systematic review can be found are listed.

@@

(ref:drDemeniaTC-cap) __Dose-response meta-analysis of total cholesterol on all-cause dementia__

@@

(ref:drAdLDL-cap) __Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease__

@@

(ref:minFU-cap) __Illustration of minimum follow-up period in two study designs__ - Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up. In contrast, Panel B illustrates the time- varying analysis used in Chapter \@ref(cprd-analysis-heading), which makes it challenging to define an unbiased minimum period of follow-up.

@@

<!-- With these caveats in mind, below I present a sensitivity analysis of the association of statins with dementia outcomes, enforcing a minimum 10-year period of follow-up from statin initiation in those prescribed a statin.  -->

<!----------------------------------------------------------------------------->
<!-- (ref:cprdMinFu-cap) Sensitivity analysis showing the results of a re-analysis of the CPRD data enforcing a minimum follow-up period of 10 years in the statin group. Events occurring within 10 years of inititating statins were discarded, but the participant-time-at-risk was maintained. No minimum follow-up period was applied in those never taking a statin, due to the difficulties in defining the start date for the follow-up period, as discussed in the text above. -->

<!-- (ref:cprdMinFu-scap) Sensitivity analysis of the CPRD data with a 10 year minimum period of follow-up. -->

<!-- ```{r cprdMinFu, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdMinFu-cap)', out.width='100%', fig.scap='(ref:cprdMinFu-scap)'} -->
<!-- knitr::include_graphics(file.path("figures/hold.png")) -->
<!-- ``` -->
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
(ref:missingMatrix-caption) __Overview of missing data in the IPD analysis__ - Missing variables/values across cohorts included in the IPD analysis. Missing variables are denoted using a "-", while missing values are described as N (%). Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.

(ref:missingMatrix-scaption) Overview of missing data in the IPD analysis

@@

<!----------------------------------------------------------------------------->
(ref:ipdDementiaDef-caption) __Definition of dementia outcomes in IPD meta-analysis__ - The criteria used to define dementia outcomes across cohorts included in the individual participant data meta-analysis are listed below. Note the codes used to define dementia and related outcomes in the HES data as part of the Whitehall II cohort were taken from a previously published analysis.[@russ2014]

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:addTable1-caption) __Elicited bias distributions__ -  Distributions of bias, defined by position and variance terms, assigned by four independent experts to attrition and detection bias in a single study. This data was obtained from a previous publication,[@turner2009] and represents an illustrative subset of the larger dataset.

(ref:addTable1-scaption) Elicited bias distributions

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:addTable2-caption) __Elicited bias distributions, averaged across experts__ - The expert-averaged position and variance values for two example bias domains (attrition and detection) are shown. These values were obtained by averaging the absolute of the values contained in \@ref(tab:addTable3-table) across the four experts.

(ref:addTable2-scaption) Expert-elicited bias distributions, averaged across experts

@@

I then took the average and maximum of the expert-averaged position and variance values. The results of this for the example data are presented in Table \@ref(tab:addTable3-table). 
&nbsp;<!----------------------------------------------------------------------->  
(ref:addTable3-caption) __Mean and maximum bias distributions, using example data__ - The mean and maximum of position and variance values desribed in Table \@ref(tab:addTable3-table) were calculated to give the average and maximum bias adjustment across studies and domains of bias.

(ref:addTable3-scaption) Mean and maximum bias distributions, using example data

@@

&nbsp;<!----------------------------------------------------------------------->  
(ref:turnerEstimates-caption) __Mean and maximum distributions for bias and indirectness, using full data__ - Using all data resulting from the elicitation exercise reported in _Turner et al_[@turner2009], I calculated mean and maximum distributions for bias and indirectness using the method described above. Note I did not calculate values for additive indirectness, as in my analysis, all indirectness was assumed to be proportional.

(ref:turnerEstimates-scaption) Mean and maximum distributions for bias and indirectness, using full data

@@

(ref:fpLdlAdComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease under two different scenarios of additive bias.__ Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. Scenario 2: position value between the additive distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels. See Section \@ref(tri-bias-assign) for more details.

(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease under two different scenarios of additive bias.
```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
```

(ref:fpTgVaDComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia under two different scenarios of prior distributions of bias.__ Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. Scenario 2: position value between the additive distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels. See Section \@ref(tri-bias-assign) for more details.

(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia under two different scenarios of prior distributions of bias.

@@

<!-- TODO Need to complete this sections -->
The `robvis` package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.

@@

\blandscape
<!----------------------------------------------------------------------------->
(ref:biasData-caption) __Example `robvis` dataset__ - First five assessments contained in `data_rob2`, an example dataset for the Risk of Bias 2 tool for randomised controlled trials available via the `robvis` package.

(ref:biasData-scaption) Example `robvis` dataset

@@

<!----------------------------------------------------------------------------->
(ref:biasDirectionData-caption) __Example bias direction dataset__ - Example risk-of-bias data illustrating the structure required for bias direction plots. $d_ij$, $d_id$, and $d_it$ define the extent (Serious, Moderate, Low), direction (right or left), and type (additive or proportional) of bias in the $i$th domain. Note that, because of the wide nature of the data, I have abbreviated the data in order to display it. A key for interpreting the data can be found below the table.

(ref:biasDirectionData-scaption) Example bias direction dataset

@@

<!----------------------------------------------------------------------------->
(ref:robSummary-cap) __Example risk-of-bias summary barplot__ - Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above. Note that this plot is unweighted and shows the _proportion of studies_ at each level of bias, but an option exists with `robvis` to create a barplot weighted by the _proportion of evidence_ at each level of bias.

@@

<!----------------------------------------------------------------------------->
(ref:robTraffic-cap) Example risk-of-bias traffic-light plot - Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
